\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{comment}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{url}
\usepackage{cite}
\usepackage{flushend}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{A Multi-Representation Ensemble Approach to Classifying Vocal Diseases}
\author{\IEEEauthorblockN{Mingxuan Ju, Zhengkai Jiang, Yufan Chen and Soumya Ray}
\IEEEauthorblockA{Department of Electrical Engineering and Computer Science, Case Western Reserve University, Cleveland, OH 44106}
\IEEEauthorblockA{Email: {\{mxj255, zxj89, yxc775, sray\}@case.edu}}
}
\maketitle
\begin{abstract}
The goal of the IEEE 2018 FEMH Voice Data Challenge was to develop an effective algorithmic approach to classifying voice samples as normal or pathological, and further subdivide the pathological samples into three types. We adopted a multi-representation ensemble approach to the task. We designed a pipeline with three classification stages, where each stage used a combination of supervised, semi-supervised and multiple-instance learners. This approach was able to achieve a sensitivity of 89\% and specificity of 76\% in classifying normal from pathological samples and an unweighted average recall (UAR) of 60.67\% in subclassifying pathological samples into three types.
\end{abstract}
%\tableofcontents

\input{Introduction}
%\input{Background}  % Yufan Chen
\input{Method}   % Mingxuan Ju
\input{features}
\input{Results}  % Zhengkai Jiang
\input{Conclusion}


\begin{thebibliography}{00}
	
\bibitem{b1}
 Gouyon F., Pachet F., Delerue O. (2000),On the Use of Zero-crossing Rate for an Application of Classification of Percussive Sounds, in Proceedings of the COST G-6 Conference on Digital Audio Effects (DAFX-00 - DAFX-06), Verona, Italy, December 7–9, 2000. Accessed 26 April 2011.

\bibitem{b2}
Müller, G., Möser, M. (2012). Handbook of Engineering Acoustics. Springer. p. 7. ISBN 9783540694601.

\bibitem{b3}
Grey, J. M., Gordon, J. W., 1978. Perceptual effects of spectral modifications on musical timbres. Journal of the Acoustical Society of America 63 (5), 1493–1500, doi:10.1121/1.381843

\bibitem{b4}
Beigi, Homayoon (2011). Fundamentals of Speaker Recognition. Berlin: Springer-Verlag. ISBN 978-0-387-77591-3.

\bibitem{b5}
Müller, Meinard (2015). Fundamentals of Music Processing. Springer. doi:10.1007/978-3-319-21945-5. ISBN 978-3-319-21944-8.

\bibitem{b6}
T. Giannakopoulos., pyAudioAnalysis: An Open-Source Python Library for Audio Signal Analysis, PloS One, 10, pp. 12, 2015

\bibitem{b7} 
Fabian Pedregosa, Gaël Varoquaux, Alexandre Gramfort, Vincent Michel, Bertrand Thirion, Olivier Grisel, Mathieu Blondel, Peter Prettenhofer, Ron Weiss, Vincent Dubourg, Jake Vanderplas, Alexandre Passos, David Cournapeau, Matthieu Brucher, Matthieu Perrot, Édouard Duchesnay, Scikit-learn: Machine Learning in Python

\bibitem{b8} 
Lars Buitinck1, Gilles Louppe2, Mathieu Blondel3, Fabian Pedregosa4, Andreas C. Muller5, Olivier Grisel6, Vlad Niculae7, Peter Prettenhofer8, Alexandre Gramfort4,9, Jaques Grobler4, Robert Layton10, Jake Vanderplas11, Arnaud Joly2, Brian Holt12, and Ga''el Varoquaux4, API design for machine learning software: experiences from the scikit-learn project

\bibitem{b4}
P. Kukharchik, D. Martynov, I. Kheidorov and O. Kotov, "Vocal fold pathology detection using modified wavelet-like features and support vector machines," 2007 15th European Signal Processing Conference, Poznan, 2007, pp. 2214-2218.

\bibitem{b5}
Majidnezhad, V. and Kheidorov, I., 2013. An ANN-based method for detecting vocal fold pathology. arXiv preprint arXiv:1302.1772.

\bibitem{b9}
Shih-Hau Fang, Yu Tsao, Min-Jing Hsiao, Ji-Ying Chen, Ying-Hui Lai, Feng-Chuan Lin, Chi-Te Wang,
Detection of Pathological Voice Using Cepstrum Vectors: A Deep Learning Approach,
Journal of Voice, 2018,
\bibitem{b10}
S. Ray \& M. Craven (2005).
Supervised versus Multiple-Instance Learning: An Empirical Comparison.
Appears in the Proceedings of the 22nd International Conference on Machine Learning, Bonn, Germany.
\bibitem{b11}
Far Eastern Memorial Hospital, FEMH, https://www.femh.org.tw
\bibitem{b12}
Cortes, Corinna; Vapnik, Vladimir N. (1995). "Support-vector networks". Machine Learning. 20 (3): 273–297. doi:10.1007/BF00994018.
\bibitem{b13}
Xiaojin Zhu, Zoubin Ghahramani, Learning from Labeled and Unlabeled Data with Label Propagation. 
\bibitem{b14}
Xiang Liao, Dezhong Yao and Chaoyi Li, Transductive SVM for reducing the training effort in BCI
\bibitem{b15}
Renyi, Alfréd (1961). "On measures of information and entropy" (PDF). Proceedings of the fourth Berkeley Symposium on Mathematics, Statistics and Probability 1960. pp. 547–561
\bibitem{b16}
“FAQ,” FEMH CHALLENGE. [Online]. Available: https://femh-challenge2018.weebly.com/faq.html. [Accessed: 12-Nov-2018].
\bibitem{b17}
F. Pedregosa, G. Varoquaux, A. Gramfort, V. Michel, B. Thirion, O. Grisel, M. Blondel, P. Prettenhofer, R. Weiss, V. Dubourg, J. Vanderplas, A. Passos, D. Cournapeau, M. Brucher, M. Perrot, E. Duchesnay, Scikit-learn: Machine Learning in Python., JMLR 12, pp. 2825-2830, 2011.
\bibitem{b18}
Xiaojin Zhu, and Zoubin Ghahramani, and John Lafferty., Semi-supervised Learning Using Gaussian Fields and Harmonic Functions, CMU 2003,.
\bibitem{b19}
C. Cortes and V. Vapnik, “Support-vector networks,” Machine Learning, vol. 20, no. 3, pp. 273–297, 9 1995. [Online]. Available: http://link.springer.com/10.1007/BF00994018
\bibitem{b20}
D. A. Ferrucci, et al. Building watson: An overview of the deepqa project. AI Magazine 31, 59-79 (2010). Available: https://www.aaai.org/Magazine/Watson/watson.php
\bibitem{b21}
Yehuda Koren, "The bellkor solution to the netflix grand prize", Netflix prize documentation, vol. 81, 2009.
\bibitem{b22}
R. Collobert, F. H. Sinz, J. Weston, L. Bottou, "Large scale transductive SVMs", J. Mach. Learn. Res., vol. 7, pp. 1687-1712, 2006.
\bibitem{b23}
Fabian Gieseke, Antti Airola, Tapio Pahikkala, and Oliver Kramer. Fast and Simple Gradient-Based Optimization for Semi-Supervised Support Vector Machines. Neurocomputing (ICPRAM 2012 Special Issue) 123(10):23-32, 2014. 
\bibitem{b24}
Fabian Gieseke, Antti Airola, Tapio Pahikkala, and Oliver Kramer. Sparse Quasi-Newton Optimization for Semi-Supervised Support Vector Machines. In Proceedings of the 1st International Conference on Pattern Recognition Applications and Methods (ICPRAM 2012). 2012, 45-54. 
\bibitem{b25}
T. Cover and J. Thomas, Elements of information theory. New York: John Wiley \& Sons, 2006.
\bibitem{b26}
Rafael George Amado, Jozue Vieira Filho, Pitch detection algorithms based on zero-cross rate and autocorrelation function for musical notes, IEEE, July 2008
\bibitem{b27}
Chenn-JungHuang,Yi-JuYang, Dian-XiuYang,You-JiaChen, Frog classification using machine learning techniques, Expert Systems with Applications Volume 36, Issue 2, Part 2, March 2009, Pages 3737-3743, March 2008
\end{thebibliography}
\end{document}
