\section{Feature Extraction}
We now describe the feature set that we extract from the given audio files. These features are used with the classifiers above. Many of these features are widely used in machine learning for audio classification. The last feature, ``Number of Amplitude Peaks and Vallies" is created by us. The features are:
\begin{enumerate}
	\item Zero Crossing Rate (ZCR):\\
	The rate of sign-changes of the signal during the duration of a particular frame~\cite{b1}: $ZCR=\frac{1}{T-1}\sum_{t = 1}^{T - 1}I_{R<0}$, where $R = (s_t * s_{t-1})$ and $s$ is signal with length $T$.
	\item Energy:\\
	The sum of squares of the signal values, normalized by the respective frame length~\cite{b2}: $Energy = \sum_{i = 1}^{N} \frac{s_i^2}{|s_i|} $, where $N$ is the total number of blocks of signals and, $s_i$ is the signal in frame $i$.
	\item Entropy of Energy (EE):\\
	The entropy of sub-frames' normalized energies. It can be interpreted as a measure of abrupt changes.~\cite{b2} Setting number of sub-frames $n$ to $10$, we calculate EE by: EE = $\frac{(\frac{L}{n})^2}{Eol +\epsilon} \log_{2}({(\frac{(\frac{L}{n})^2}{Eol +eps} + eps})$, where $L$ is the length of audio signal, $\epsilon$ is the learning rate and $Eol$ is the total energy of this signal.
	\item Spectral Centroid (SC):\\
	It indicates where the "center of mass" of the spectrum is located. Perceptually, it has a robust connection with the impression of "brightness" of a sound~\cite{b3}:  $SC = \frac{\sum_{n = 0}^{N - 1} f(n)x(n)}{\sum_{n = 0}^{N - 1} x(n)}$, where $f(n)$ is the frequency of current bin and $x(n)$ is weighted frequency value.
	\item Spectral Energy (SE):\\
	Entropy of the normalized spectral energies for a set of sub-frames.~\cite{b3}: $SE = \sum_{i = 1}^{N} \frac{1}{N} |x(s_i)|^2$, where $x(s_i)$ is the average amplitude of sub-frame $s_i$.\\
	\item Spectral Spread (SS):\\
	The second central moment of the spectrum~\cite{b3}:  SS = $\sqrt{\frac{\sum_{k = 0}^{\frac{N}{2}} (f(k)-SC)^2 |x(k)|^2}{\sum_{k = 0}^{\frac{N}{2}} |x(k)|^2 }}$, where f(k) is the frequency at k, N is the total length of the frame and x(k) os weighted frequency value \\
	\item Spectral Entropy:\\
	Entropy of the normalized spectral energies for a set of sub-frames\cite{b3}: $SpEn = -\sum_{i = 1}^{n} \frac{\frac{1}{N} |x(s_i)|^2}{\sum_{i}^{}\frac{1}{N} |x(s_i)|^2} \ln\frac{\frac{1}{N} |x(s_i)|^2}{\sum_{i}^{}\frac{1}{N} |x(s_i)|^2}$.
	\item Spectral Flux:\\
	The squared difference between the normalized magnitudes of the spectra of the two successive frames~\cite{b3} We calculate Spectral Flux by equation: Spectral Flux = $\int_{\pi_+}^{} I * \cos(\theta(n)) dw(n)$, where I is indicator function of integration that extends only over the solid angles of relevant hemisphere, $\theta(n)$ denotes the angle between n and prescribed direction. More intuitively, this feature describes envelope of the spectrum of a signal.
	\item Spectral Rolloff:\\
	The frequency below which 90\% of the magnitude distribution of the spectrum is concentrated~\cite{b3}: $SpRo = \arg \min \sum_{i = 1}^{f_c} m_i \geq \sum_{i = 1}^{N}0.9 m_i$, where $f_c$ is the rolloff frequency and $m_i$ is the magnitude of the $i^{th}$ frequency component of the spectrum. 
	\item Mel Frequency Cepstral Coefficients(MFCCs):\\
	Mel Frequency Cepstral Coefficients form a cepstral representation where the frequency bands are not linear but distributed according to the mel-scale.~\cite{b4}:  $MFCC = \sum_{k = 0}^{\frac{N}{2}}\log |s(n)| H_i(k\frac{2\pi}{N_p})$, where $N$ is the frame length, $s(n)$ is Discrete Fourier transform signal, $H_i$ is the critical band filter at $i^{th}$ coefficient, and $N_p$ is the number of points used in the short term Discrete Fourier transform. More detailed description of MFCC can be found in~\cite{b9}.
	\item Chroma Vector:\\
	A 12-element representation of the spectral energy where the bins represent the 12 equal-tempered pitch classes of western-type music (semitone spacing).\cite{b5} We calculate this by detecting the tone height and chroma of certain segment, and assign each element the vector it falls into.
	\item Chroma Deviation:\\
	The standard deviation of the 12 chroma coefficients.~\cite{b5}
	\item Number of Amplitude Vally and Peak:\\
	The number of amplitude peaks and vallies. We extract this feature by counting the number of frames where its amplitude derivative is 0. %The mathematical description of this feature is : $ \sum_{t = 1}^{N-1}  I_{dR=0}$, where dR is the derivative of amplitude curve, and N is the total length of this frame.\\
\end{enumerate}
Because we had a very small training set, for the supervised learning algorithms, overfitting was a concern especially later in the pipeline where there were fewer training examples. To reduce this effect, we used mutual information based feature selection~\cite{b25} for the SVMs (linear and RBF) and trained these models on 50\% of the features.

First 13 features are widely used in the field of machine learning for audio classification\cite{b26}\cite{b27}. We utilize an existing library\cite{b6} that implements first those features. The last feature Local Amplitude Minimum is introduced by us to help classifiers distinguishing normal audio and abnormal audio, which turns out to be extremely efficient.